---
title: Tech
author: John
date: '2020-02-27'
draft: false
categories:
  - R
tags:
  - R Markdown
---

<div id="tech-app" role="main" style="width: 100%; min-width: 800px;">
&nbsp;
</div>

# [SveltR](https://github.com/Real-Currents/SveltR)

## A blogdown boilerplate for creating truly epic visualizations

```{r setup, include=FALSE}
options(warn = -1)
working_dir <- getwd()
print(working_dir)
print(grepl("/content", getwd(), ignore.case = TRUE))
if (grepl("/content", getwd(), ignore.case = TRUE)) {
  working_dir <- stringr::str_replace(getwd(), "/content", "")
  setwd(working_dir)
  print("")
}
if (!require("knitr")) {
  install.packages("knitr")
  library("knitr")
}
knitr::opts_chunk$set(cache = TRUE)
knitr::opts_chunk$set(echo = TRUE)

```

This is a boilerplate for using [blogdown (R Markdown x Hugo)](https://github.com/rstudio/blogdown/) as a static site generator and [Svelte](https://svelte.dev/) as your reactive app engine. This project is released under the [MIT license](LICENSE). Please make sure you understand its implications and guarantees.
<br />

## Enjoy!! 🦊

This page is the product of an R Markdown document and an embedded Svelte app. The `<div id="test-app"></div>` HTML tag  embedded in this page contains the "test-app" id attribute which is a DOM element id that `TestApp.svelte` has been instructed to find in order to instantiate the interactive graphics above. To learn more about developing Svelte applications see <https://svelte.dev/tutorial/basics>. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

You can embed an R code chunk like this:

```{r echo}
print(mean(1 : 5))

Sys.getenv("R_HOME")

r_profiles <- c(file.path(Sys.getenv("R_HOME"), "etc", "Rprofile.site"),
                file.path(Sys.getenv("R_HOME"), "etc", "Rprofile"),
                file.path(Sys.getenv("R_HOME"), "library", "base", "R", "Rprofile") )

Filter(file.exists, r_profiles)

.libPaths()
```
<br />

## Including Plots

You can also embed (static) plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

<div class="r-mapping">
Use R's geospatial packages to plot data on maps. For the following example, you will need to have installed the following native libraries on the host operating system:
pandoc gdal geos proj udunits2:

```{r mapping, echo=FALSE}
options(warn=-1)  # versions of GEOS runtime 3.7.2-CAPI-1.11.2 and GEOS at installation 3.7.1-CAPI-1.11.1 differ
if (!require("sp")) {
  install.packages("sp")
}
if (!require("rgdal")) {
  install.packages("rgdal")
}
if (!require("rgeos")) {
  install.packages("rgeos")
}
if (!require("sf")) {
  install.packages("sf")
}
options(warn=0)
if (!require("maptools")) {
  install.packages("maptools")
} else {
  options(warn=-1)
  require(sp)
  require(rgdal)
  require(rgeos)
  options(warn=0)
  require(maptools)

  data(wrld_simpl)
  xlim <- c(-130,-60)
  ylim <- c(35,50)
  plot(wrld_simpl,xlim=xlim,ylim=ylim,col='olivedrab3',bg='lightblue')
  plot(wrld_simpl)
  coords <- matrix(c(-122.92,-79.4, 49.277,43.66),ncol=2)

  coords <- matrix(c(-122.92,-79.4, 49.277,43.66),ncol=2)
  coords <- coordinates(coords)
  spoints <- SpatialPoints(coords)
  df <- data.frame(location=c("SFU","UofT"))
  spointsdf <- SpatialPointsDataFrame(spoints,df)
  plot(wrld_simpl) + plot(spointsdf,add=T,col=c('red','blue'),pch=16)
}
```
</div>

## Embedding JSON data in HTML

If the output target is HTML, R has some methods for turning R data into JavaScript or JSON data and printing the results within HTML tags:
```{r car_data}

head(mtcars)
```

The mtcars sample dataset printed above has been serialized to JSON and added to a `<script>` tag contained within a `<div id="car_data_in_html">`.
<div class="r-data">

```{r car_data_in_html, results = 'asis'}
require(jsonlite)

# print without tabs so R markdown will add it to the DOM tree of the resulting page
cat(paste('<div id="car_data_in_html"><script type="application/json">', toJSON(mtcars), '\n</script>\n</div>', sep=""))
```

```{r, echo = FALSE, results = 'asis'}
# add tabs to tags, to pre print code results
cat(paste('\n\t<div id="car_data_in_html">\n\t\t<script type="application/json">', toJSON(mtcars), '\n\t\t</script>\n\t</div>', sep=""))
```
</div>


Note the specification of the `type="application/json"` attribute, which prevents the browser from evaluating the contents of the `<script>` tag as JavaScript (if that is intended) and allows some other code block to call:

    <script>
      var data = JSON.parse(document.getElementById('car_data_in_html').children[0].innerHTML);
    </script>

<br />

## Run Python with Reticulate

It is also possible to include Python code chunks in R Markdown, by first loading the `reticulate` package (in R):
```{r prepare_python, echo = TRUE}
# Load reticulate package for running python
if (!require("reticulate")) {
  install.packages("reticulate")
  reticulate::conda_python(envname = "r-reticulate")
  reticulate::use_condaenv(condaenv = "r-reticulate", required = TRUE)
}

reticulate::py_install(c("matplotlib"))

py_sys <- import("sys")
print(py_sys$path)
cat(list.files(py_sys$path)[grepl("matplot", list.files(py_sys$path))])
```

... and then writing the python code;
```{python data_test}
data = {"foo": {"bar": "baz"}}
string = "Reticulate"

for index, letter in enumerate(string):
    print((letter, index))
```

```{python pyplot}
import sys

sys.path

try:
  import matplotlib.pyplot as plt
  import numpy as np

  # %matplotlib inline
  # %config InlineBackend.figure_format = 'svg'
  t = np.linspace(0, 20, 500)

  plt.plot(t, np.sin(t))
  plt.show()

except Exception as e:
  print(e)
```
